%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Qualitest} % Organization
    {Greensboro, North Carolina} % Location
    {Jul. 2022 - Jun. 2023} % Date(s)
	{
		\begin{cvitems}
      \item {Worked remotely with a team of senior developers under an Agile Scrum environment.}
      \item {Designed automated tests, executed tests against software environment, and filed bug reports when actual results differed from expected}
      \item {Wrote automated tests to test API and other web services.}
      \item {Documented work history under user story tickets and attended standup meetings with colleagues.}
      \item {Coordinated assigned work with Git version control and Jira.}
      \item {Overall responsibility of the Software Engineer role is to find problems, think about problems, and solve problems.}
		\end{cvitems}
	}

%---------------------------------------------------------
  \cventry
    {Independent Contractor Computer Science and Discrete Math Tutor} % Job title
    {Wyzant} % Organization
    {REMOTE} % Location
    {Nov. 2019 - PRESENT} % Date(s)
    {
    	\begin{cvitems}
			\item {Same experience as my other tutoring position.}
		\end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Independent Contractor Computer Science and Discrete Math Tutor} % Job title
    {Varsity Tutors} % Organization
    {REMOTE} % Location
    {Mar. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided assistance in Computer Science and Discrete Math for over 300 international clients from a variety of demographics on the online tutoring platform: varsitytutors.com.}
        \item {Worked in an environment that encouraged ongoing learning. Experienced in a variety of professional environments: Primary and Secondary Education, College, Coding Boot-Camps, and Professional level.}
        \item {Educator of Introduction to Computer Science for programming languages Java, C, C++, PHP, Python, JavaScript, Snap, and Scratch. Lectures are done on video calls through the online platform and content is managed on repl.it.}
        \item {Assisted in difficult Discrete Math and CS problems, enriched those topics by integrating the two. Practice is sometimes done through\\codewars.com.}
        \item {Understands the common weaknesses in current Computer Science curriculum's and improved student understanding by providing rare to find insight.}
        \item {Provided College and Career mentor-ship for students of all ages.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Introduction to Computer Science (CSC - 130) Lab assistant} % Job title
    {UNCG Computer Science Department} % Organization
    {Greensboro, North Carolina} % Location
    {Jan. 2018 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted CSC-130 students with issues with software and further questions on assignments.}
        \item {Proctored lab exams and provided advice for future courses.}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}
